### 2025-01-13 skripsi/abstract.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

%\chapter{ABSTRACT}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{center}
\textbf{\large  ABSTRACT}\\[0.5cm]
\textbf{\large TITLE}\\[0.5cm]
\textbf{by}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent In general, Abstract is a translation of Abstrak. However, appropriate paraphrase may need some words or sentences whose meanings are close enough to those written in Abstrak.

\noindent Key words: \keywords

>>>>

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{center}
\textbf{\large  ABSTRACT}\\[0.5cm]
\textbf{\large \judulcapitalized}\\[0.5cm]
\textbf{by}\\
\textbf{\penulis}\\
\textbf{NIM:\@\nim}\\[2em]
\end{center}

\noindent Numerical models of systems are a crucial part of science and engineering. The use of machine learning in this space for operator learning provides an alternative as data-driven surrogates. The Fourier Transform provides a key component for learning the relationship between a function and its derivatives. Building on Spectral Neural Operators (SNO), we propose a Support Vector Machine (SVM) based framework to learn the underlying governing equations of a system based on data. We study the viability and interpretability of the proposed framework on the derivative equation and the Burgers' equation. The model is able to learn from mathematically correct random data and is able to partially generalize to an exact solution of the Burgers' equation. The learned model is interpreted and verified to have learned the correct contributions of the input function coefficients to the output function coefficients.

\noindent Keywords: \keywords{}

### 2025-01-13 skripsi/abstrak.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

%\chapter{ABSTRAK}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRAK}
\begin{center}
\textbf{\large  ABSTRAK}\\[0.5cm]
\textbf{\large JUDUL ABSTRAK}\\[0.5cm]
\textbf{Oleh}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis. Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan. Abstrak ditulis menjelang akhir penyelesaian penulisan buku TA.

Secara umum, abstrak memuat beberapa komponen penting, yaitu: konteks atau cakupan pekerjaan penelitian, tujuan penelitian, metodologi yang digunakan selama penelitian, hasil-hasil penting yang dapat ditambahkan dengan implikasinya, dan simpulan dari penelitian. Dengan demikian, suatu abstrak tidak dapat dituliskan apabila penelitian belum mencapai hasil tertentu, apalagi kalau penelitiannya pun belum dilakukan.

Panjang abstrak sebaiknya dicukupkan dalam satu halaman, termasuk kata kunci. Tiga kata kunci dipandang cukup, yang masing-masingnya memuat paduan kata utama, yang dapat merepresentasikan isi Abstrak. Halaman Abstrak tidak memuat informasi judul dan penulis, sehingga tidak secara langsung dapat digunakan sebagai lembaran Abstrak Sidang TA yang disediakan untuk hadirin, yang memerlukan tambahan (sekurangnya) dua informasi tersebut.

\noindent Kata kunci: \katakunci

>>>>

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRAK}
\begin{center}
\textbf{\large  ABSTRAK}\\[0.5cm]
\textbf{\large Aproksimasi Solusi \textit{Govering Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
\textbf{Oleh}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent Model numerik sebuah sistem merupakan bagian penting dari ilmu pengetahuan dan \textit{engineering}. Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}. \textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya. Berdasarkan \textit{Spectral Neural Operators (SNO)}, kami mengusulkan kerangka kerja berbasis \textit{Support Vector Machine (SVM)} untuk mempelajari persamaan dasar yang mengatur suatu sistem berdasarkan data. Kami mempelajari kelayakan dan interpretabilitas kerangka kerja yang diusulkan pada persamaan turunan dan persamaan Burgers. Model ini mampu belajar dari data acak yang secara matematis benar dan sebagian mampu melakukan generalisasi ke solusi eksak dari persamaan Burgers. Model yang dipelajari diinterpretasikan dan diverifikasi untuk mempelajari kontribusi yang benar dari koefisien fungsi masukan terhadap koefisien fungsi keluaran.
% \noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis. Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan. Abstrak ditulis menjelang akhir penyelesaian penulisan buku TA.

% Secara umum, abstrak memuat beberapa komponen penting, yaitu: konteks atau cakupan pekerjaan penelitian, tujuan penelitian, metodologi yang digunakan selama penelitian, hasil-hasil penting yang dapat ditambahkan dengan implikasinya, dan simpulan dari penelitian. Dengan demikian, suatu abstrak tidak dapat dituliskan apabila penelitian belum mencapai hasil tertentu, apalagi kalau penelitiannya pun belum dilakukan.

% Panjang abstrak sebaiknya dicukupkan dalam satu halaman, termasuk kata kunci. Tiga kata kunci dipandang cukup, yang masing-masingnya memuat paduan kata utama, yang dapat merepresentasikan isi Abstrak. Halaman Abstrak tidak memuat informasi judul dan penulis, sehingga tidak secara langsung dapat digunakan sebagai lembaran Abstrak Sidang TA yang disediakan untuk hadirin, yang memerlukan tambahan (sekurangnya) dua informasi tersebut.

\noindent Kata kunci: \katakunci{}

### 2025-01-13 skripsi/chapter1.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

% !TEX root = ./skripsi.tex
\chapter{INTRODUCTION}
\section{Background}\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also define systems using PDEs. PDEs are also used outside the physical sciences. In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market. In ecology, PDEs are used to model population growth which is useful for modelling location dependent carrying capacity. This is used to model species distribution which can help develop better conservation policies. In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment \autocite{jinDetectingInteractionUrban2023}. Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}. PDEs have a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.

An increasingly critical use of PDEs is in Numerical weather prediction (NWP). The information weather forecasts provide is an integral part of modern life. Many sectors rely on timely and accurate weather forecasts. Individuals, day to day rely on forecasts for a range of different decisions ranging from activities they can do to personal safety from extreme weather. The weather also affects retail as consumer behavior change with whether it is rain or shine \autocite{tianImpactWeatherConsumer2021,tianPredictingConsumerVarietyseeking2018,govindWeatherAffectPreference2020,moonWeatherSensitivityAnalysis2018}. Similarly, the types of transportation people use and operational decisions changes with the weather \autocite{lepageImpactWeatherActivities2021,nurmiExpectedImpactsValue2013}. Another critical sector is agriculture, where extreme weather events and changes in climate threatens the food supply \autocite{cogatoExtremeWeatherEvents2019,malhiImpactClimateChange2021,anwarAdaptingAgricultureClimate2013}. As the climate continues to warm and extreme weather events increase in frequency, the mitigation for these events become all the more important \autocite{ClimateChange20222023}. Because of this, forecasting is critical in making accurate decisions for policymakers and warnings of extreme weather events for civilians \autocite{astithaExtremeWeatherForecasting2023,stottAttributionExtremeWeather2016}. A major challenge is the fact that observations of weather can be sparse in the sense that observations are localized and do not cover entire areas \autocite{wilbyRainfallTemperatureEstimation2013,monmonierAirApparentHow1999,galkinAssimilationSparseContinuous2020}. This lack of spatially distributed meteorological information hampers decision-making on areas to be prioritized and what to prioritize based on location. For example, weather stations can only observe their immediate surroundings. And they are for the most part stationary. Even more mobile observation platforms like satellites only show the portion of the surface the satellite can see at any one time such as in \lccref{fig:satellite_image_coverage}. While accumulating observations through more satellite passes is possible, this, however, means short-lived features may not be observed. As impoverished regions often are the most data sparse, the effect compounds on the fact that for impoverished regions, scarce resources need to be effectively and efficiently applied. To this end, numerical models are employed to model a more representative view by using known physics such as the compressible Euler equations and statistical models \autocite{mengaldoCurrentEmergingTimeIntegration2019,kwasniokDatabasedStochasticSubgridscale2012}. The next step is in forecasting future weather which in itself is a challenge. The information this could provide is invaluable because it means planning for future weather is possible.

\begin{figure}[ht] %h means here!
    \centering
    \includegraphics[width=1.0\linewidth]{figures/snapshot_nasa_airs_aqua_2024_05_21T00_00_00Z.jpg}
    \caption{Daytime and nighttime surface air temperature from observations by the AIRS instrument onboard the NASA AQUA satellite. This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024. Notice that parts of the globe, especially near the equator have not been observed. This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}
\end{figure}

>>>>

% !TEX root = ./skripsi.tex
\chapter{INTRODUCTION}
\section{Background}\label{sec:background}
% TODO:talk about mathematical models and governing equations here instead. PDEs can be talked later as a subset of governing equations
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

Many other fields in physics such as waves, quantum dynamics, fluid dynamics, elastics, and many more also model systems using PDEs. PDEs are also used outside the physical sciences. In Finance, the Black-Scholes-Merton or Black-Scholes equation models the dynamics of the financial market. In ecology, PDEs are used to model population growth which is useful for modelling location dependent carrying capacity. This is used to model species distribution which can help develop better conservation policies. In the social sciences, PDEs such as the cross-diffusion model is used to explore the evolution of the urban environment \autocite{jinDetectingInteractionUrban2023}. Crowd dynamics is another field where researchers have found it useful to model using PDEs \autocite{mukherjeeLagrangianApproachModeling2015,hughesFlowLargeCrowds2000}. PDEs have a variety of applications, ranging from bird flocks, pedestrian crowds, to robotic swarms \autocite{gongCrowdDynamicsModeling2023}.

An increasingly critical use of PDEs is in Numerical weather prediction (NWP). The information weather forecasts provide is an integral part of modern life. Many sectors rely on timely and accurate weather forecasts. Individuals, day to day rely on forecasts for a range of different decisions ranging from activities they can do to personal safety from extreme weather. The weather also affects retail as consumer behavior change with whether it is rain or shine \autocite{tianImpactWeatherConsumer2021,tianPredictingConsumerVarietyseeking2018,govindWeatherAffectPreference2020,moonWeatherSensitivityAnalysis2018}. Similarly, the types of transportation people use and operational decisions changes with the weather \autocite{lepageImpactWeatherActivities2021,nurmiExpectedImpactsValue2013}. Another critical sector is agriculture, where extreme weather events and changes in climate threatens the food supply \autocite{cogatoExtremeWeatherEvents2019,malhiImpactClimateChange2021,anwarAdaptingAgricultureClimate2013}. As the climate continues to warm and extreme weather events increase in frequency, the mitigation for these events become all the more important \autocite{ClimateChange20222023}. Because of this, forecasting is critical in making accurate decisions for policymakers and warnings of extreme weather events for civilians \autocite{astithaExtremeWeatherForecasting2023,stottAttributionExtremeWeather2016}.
% TODO: do i need this? because my project doesn't address this. at least not directly. I can mention this as context for where other ML research in weather has gone.
A major challenge is the fact that observations of weather can be sparse in the sense that observations are localized and do not cover entire areas \autocite{wilbyRainfallTemperatureEstimation2013,monmonierAirApparentHow1999,galkinAssimilationSparseContinuous2020}. This lack of spatially distributed meteorological information hampers decision-making on areas to be prioritized and what to prioritize based on location. For example, weather stations can only observe their immediate surroundings. And they are for the most part stationary. Even more mobile observation platforms like satellites only show the portion of the surface the satellite can see at any one time such as in \lccref{fig:satellite_image_coverage}. Notice that parts of the globe, especially near the equator have not been observed. While accumulating observations through more satellite passes is possible, this, however, means short-lived features may not be observed. As impoverished regions often are the most data sparse, the effect compounds on the fact that for impoverished regions, scarce resources need to be effectively and efficiently applied. To this end, numerical models are employed to model a more representative view by using known physics such as the compressible Euler equations and statistical models \autocite{mengaldoCurrentEmergingTimeIntegration2019,kwasniokDatabasedStochasticSubgridscale2012}. The next step is in forecasting future weather which in itself is a challenge. The information this could provide is invaluable because it means planning for future weather is possible.
\begin{figure}[H] 
    \centering
    \includegraphics[width=1.0\linewidth]{figures/snapshot_nasa_airs_aqua_2024_05_21T00_00_00Z.jpg}
    \caption{Daytime and nighttime surface air temperature from observations by the AIRS instrument onboard the NASA AQUA satellite. This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024. This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}
\end{figure}

### 2025-01-13 skripsi/chapter2.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work

The convolution term behaves in an amplifying manner. For areas that have the same signs for their solution value and the space derivative, it would attract it to lower values. For areas with differing signs for the solution value and space derivative, it would attract it to a higher value. As a whole this would make the solution tend toward large negative gradients and discourage large positive gradients. As the negative gradient grows, if unimpeded by the advection term, it would eventually lead to the formation of a shock wave moving to the positive x direction. Finally, the forcing term affects the time derivative directly and attract the solution toward which ever direction defined by the forcing term. %add discussion about turbulence here.
% TODO: add figure for the effects of each term on the time derivative and how the solution evolves
Solutions to the Burgers' equation can be obtained analytically. One of the most straightforward ways is the Cole-Hopf transform. Using this method, the solution to the Burgers' equation \(u\) is computed from any valid solutions of the heat equation \(\phi \). The solution of the Burgers' equation is obtained by using the Cole-Hopf transform written in \lccref{eq:cole_hopf}. However, this limits the range of possible solutions because of the requirement of a valid heat equation solution. For a wider range of solutions, numerical methods are predominantly used to solve the initial value problem for the Burgers' equation. This can be done by computing the time derivative term from the other terms. However, both the convection and advection terms create a challenge in solving the equation numerically. For small viscosity values, the equation is dominated by the convection term. And as previously mentioned this means the development of sharp gradients and possibly shock waves. As the gradient become sharper, the solution would require finer and finer time steps in order to stay at a consistent error for each step, otherwise the solution can become unstable.
\begin{align}
  u = -2\nu\frac{\phi_x}{\phi}\label{eq:cole_hopf}
\end{align}

High viscosity values introduce a similar issue. The problem comes from rapidly varying large values introduced by the second derivative. This is a product of the \enquote{amplification} caused by derivatives which is compounded by higher orders. The rapid variation also mean that smaller time steps would need to be used by standard numerical solvers. For numerical solvers, such as the forward Euler method we discussed earlier, insufficiently fine time steps can lead to numerical instability. This imposes a constraint on how large the time steps and or on how the numerical solvers can treat these equations. The differential equations that cause this issue are called stiff PDEs. To overcome these challenges, specialized numerical solvers for stiff PDEs have been developed \autocite{kassamFourthOrderTimeSteppingStiff2005}.

@@

The interplay between the governing equations of weather are very complex. In addition, some constituting equations like the Navier-Stokes, can be very nonlinear. These are some reasons why analytical solutions for the governing equation are not feasible for realistic scenarios. Today, the weather is modeled by numerical methods. Initially, many numerical models that were in use were based on the Finite Differences Method (FDM). After 1972, other approaches regained interest, namely the spectral methods \autocite{puNumericalWeatherPrediction2018,mengaldoCurrentEmergingTimeIntegration2019}. Much more recently, other advances include ensemble forecasting where multiple models represent the probabilistic distribution that needs to be accounted for. Another development is advanced data assimilation methods for various observational data sources \autocite{parkDataAssimilationAtmospheric2013}. Due to the size differences involved with simulating the weather, some parts such as turbulence or the presence of aerosols adds further challenges. Many operational models, use approximations such as turbulence closure because the unknowns outnumber the equations. Due to these challenges, there has been research into the use of machine learning and other statistical methods for this specific area \autocite{langAIFSECMWFDatadriven2024,bonevSphericalFourierNeural2023}. Machine learning-based approaches provide the ability to predict the weather with increasing accuracy and speed using a black box model which complements the physics-based models \autocite{biAccurateMediumrangeGlobal2023}. Ongoing research and technological developments continue to refine these models, aiming for more precise and reliable weather forecasts.
% TODO: talk about inverse and forward problems

@@

The Fourier series can be represented in two ways, the first is the real representation by using sine and cosines as the basis functions in the series shown in \lccref{eq:fourier_series_sine_cosine}. The second representation is the complex representation which uses Euler's formula as the basis functions shown in \lccref{eq:fourier_series_complex}. Both of these are equivalent and are just the different representations. The relationship between the two representations is defined in \lccref{eq:fourier_coefficient_equivalency}.
\begin{align}
  f(x)=       & \hat{a}_0 + \sum_{k=0}^{\infty} \hat{a}_k\cos(2\pi kx) + \hat{b}_k\sin(2\pi kx)\label{eq:fourier_series_sine_cosine} \\
  f(x)=       & \sum_{k=-\infty}^{\infty} \hat{c}_k e^{2\pi ikx}\label{eq:fourier_series_complex}                                    \\
  \hat{c}_k = & \begin{cases}
                  \hat{a}_0,               & k = 0 \\
                  (\hat{a}_k-\hat{b}_k)/2, & k > 0 \\
                  (\hat{a}_k+\hat{b}_k)/2, & k < 0 \\
                \end{cases}\label{eq:fourier_coefficient_equivalency}
\end{align}

@@

% Derivatives and antiderivatives of fourier series
The Fourier series has an important property that is very important to this study. Taking the derivative of the Fourier series in \lccref{eq:fourier_series_complex} with respect to \(x\) results in \lccref{eq:fourier_series_complex_derivative}. Assuming we represent the derivative function is represented as another Fourier series with coefficients \(\hat{f'}_k\), the derivative coefficients can be computed from the coefficients of the original function \(f\) as shown in \lccref{eq:fourier_coeff_derivative}. This shows that the derivative of a Fourier series can be obtained trivially by simply multiplying the coefficients with the coefficients of the basis function exponents. The antiderivative can similarly be obtained by using the same relation and dividing the coefficients of the original function with the same scaling factor. Notice that the wave number is included in the scaling factor. This means that higher frequency coefficients get scaled more. For derivatives this amplifies the higher frequencies more and the antiderivative will smooth out the function by suppressing the higher frequencies.
\begin{align}
  \dv{x}f(x)=  & \sum_{k=-N/2}^{N/2-1} \hat{c}_k (2\pi ik) e^{2\pi ikx} \label{eq:fourier_series_complex_derivative} \\
  =            & \sum_{k=-N/2}^{N/2-1} \hat{f'}_k e^{2\pi ikx}\nonumber                                              \\
  \hat{f'}_k = & (2\pi ik)\hat{c}_k\label{eq:fourier_coeff_derivative}
\end{align}

@@

% \section{Referensi dan Citation}
% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}. Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}. Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.

>>>>

The convolution term behaves in an amplifying manner. For areas that have the same signs for their solution value and the space derivative, it would attract it to lower values. For areas with differing signs for the solution value and space derivative, it would attract it to a higher value. As a whole this would make the solution tend toward large negative gradients and discourage large positive gradients. As the negative gradient grows, if unimpeded by the advection term, it would eventually lead to the formation of a shock wave. Finally, the forcing term affects the time derivative directly and attract the solution toward which ever direction defined by the forcing term. %add discussion about turbulence here.
% TODO: add figure for the effects of each term on the time derivative and how the solution evolves
Solutions to the Burgers' equation can be obtained analytically. One of the most straightforward ways is the Cole-Hopf transform \autocite{wazwazPartialDifferentialEquations2010}. Using this method, the solution to the Burgers' equation \(u\) can be computed from any valid solutions of the heat equation \(\phi \). The solution of the Burgers' equation is obtained by using the Cole-Hopf transform written in \lccref{eq:cole_hopf}. For example, one solution from this transform is shown in \lccref{eq:burgers_exact_solution} was specifically mentioned by \textcite{woodExactSolutionBurgers2006} to be complex enough to test how well numerical methods solving the Burgers' equation can handle the nonlinearity. Similar solutions and other solutions using also exists in other literature \autocite{bentonTableSolutionsOnedimensional1972,wazwazPartialDifferentialEquations2010}.
\begin{align}
  u = -2\nu\frac{\phi_x}{\phi}\label{eq:cole_hopf}
\end{align}
\begin{equation}
  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
\end{equation}

The use of the Cole-Hopf transform, however, limits the range of possible solutions because of the requirement of a valid heat equation solution. For a wider range of solutions, numerical methods are predominantly used to solve the initial value problem for the Burgers' equation. This can be done by computing the time derivative term from the other terms. However, both the convection and advection terms create a challenge in solving the equation numerically. For small viscosity values, the equation is dominated by the convection term. And as previously mentioned this means the development of sharp gradients and possibly shock waves. As the gradient become sharper, the solution would require finer and finer time steps in order to stay at a consistent error for each step, otherwise the solution can become unstable.
High viscosity values introduce a similar issue. The problem comes from rapidly varying large values introduced by the second derivative. This is a product of the \enquote{amplification} caused by derivatives which is compounded by higher orders. The rapid variation also mean that smaller time steps would need to be used by standard numerical solvers. For numerical solvers, such as the forward Euler method we discussed earlier, insufficiently fine time steps can lead to numerical instability. This imposes a constraint on how large the time steps and or on how the numerical solvers can treat these equations. The differential equations that cause this issue are called stiff PDEs. To overcome these challenges, specialized numerical solvers for stiff PDEs have been developed \autocite{kassamFourthOrderTimeSteppingStiff2005}.

@@

The interplay between the governing equations of weather are very complex. In addition, some constituting equations like the Navier-Stokes, can be very nonlinear. These are some reasons why analytical solutions for the governing equation are not feasible for realistic scenarios. Today, the weather is modeled by numerical methods. Initially, many numerical models that were in use were based on the Finite Differences Method (FDM). After 1972, other approaches regained interest, namely the spectral methods \autocite{puNumericalWeatherPrediction2018,mengaldoCurrentEmergingTimeIntegration2019}. Much more recently, other advances include ensemble forecasting where multiple models represent the probabilistic distribution that needs to be accounted for. Another development is advanced data assimilation methods for various observational data sources \autocite{parkDataAssimilationAtmospheric2013}. Due to the size differences involved with simulating the weather, some parts such as turbulence or the presence of aerosols adds further challenges. Many operational models, use approximations such as turbulence closure because the unknowns outnumber the equations. Due to these challenges, there has been research into the use of machine learning and other statistical methods for this specific area \autocite{langAIFSECMWFDatadriven2024,bonevSphericalFourierNeural2023}. Machine learning-based approaches provide the ability to predict the weather with increasing accuracy and speed using a black box model which complements the physics-based models \autocite{biAccurateMediumrangeGlobal2023}. Ongoing research and technological developments continue to refine these models, aiming for more precise and reliable weather forecasts.
% TODO: talk about inverse and forward problems
% There are categories of problems when solving PDEs, The forward problem (IVP, BVP, IVBP) and the inverse problem (parameter estimation)

@@

The Fourier series can be represented in two ways, the first is the real representation by using sine and cosines as the basis functions in the series shown in \lccref{eq:fourier_series_sine_cosine}, where \(k\) is the wave number, \(L\) is the period, and \(\hat{a}_{k}\) and \(\hat{b}_{k}\) are the coefficients for the \(k\)-th wave number. The second representation is the complex representation which uses Euler's formula as the basis functions shown in \lccref{eq:fourier_series_complex} with complex valued coefficients \(\hat{c}_{k}\). Both of these are equivalent and are just the different representations. The relationship between the two representations is defined in \lccref{eq:fourier_coefficient_equivalency}.
\begin{align}
  f(x)=       & \hat{a}_0 + \sum_{k=0}^{\infty} \hat{a}_k\cos(2\pi kx/L) + \hat{b}_k\sin(2\pi kx/L)\label{eq:fourier_series_sine_cosine} \\
  f(x)=       & \sum_{k=-\infty}^{\infty} \hat{c}_k e^{2\pi ikx/L}\label{eq:fourier_series_complex}                                    \\
  \hat{c}_k = & \begin{cases}
                  \hat{a}_0,               & k = 0 \\
                  (\hat{a}_k-\hat{b}_k)/2, & k > 0 \\
                  (\hat{a}_k+\hat{b}_k)/2, & k < 0 \\
                \end{cases}\label{eq:fourier_coefficient_equivalency}
\end{align}

@@

% Derivatives and antiderivatives of fourier series
The Fourier series has an important property that is very important to this study. Taking the derivative of the Fourier series in \lccref{eq:fourier_series_complex} with respect to \(x\) results in \lccref{eq:fourier_series_complex_derivative}. Assuming we represent the derivative function is represented as another Fourier series with coefficients \(\hat{f'}_k\), the derivative coefficients can be computed from the coefficients of the original function \(f\) as shown in \lccref{eq:fourier_coeff_derivative}. This shows that the derivative of a Fourier series can be obtained trivially by simply multiplying the coefficients with the coefficients of the basis function exponents. The antiderivative can similarly be obtained by using the same relation and dividing the coefficients of the original function with the same scaling factor. Notice that the wave number is included in the scaling factor. This means that higher frequency coefficients get scaled more. For derivatives this amplifies the higher frequencies more and the antiderivative will smooth out the function by suppressing the higher frequencies.
\begin{align}
  \dv{x}f(x)=  & \sum_{k=-N/2}^{N/2-1} \hat{c}_k (2\pi ik/L) e^{2\pi ikx/L} \label{eq:fourier_series_complex_derivative} \\
  =            & \sum_{k=-N/2}^{N/2-1} \hat{f'}_k e^{2\pi ikx/L}\nonumber                                              \\
  \hat{f'}_k = & (2\pi ik/L)\hat{c}_k\label{eq:fourier_coeff_derivative}
\end{align}

@@

% \section{Referensi dan Citation}
% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \autocite{Fujita1996}. Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \autocite{hohen1964,Kim2006}. Atau untuk tiga sumber berarti \autocite{kongkanand2006,kresse1999,Leibb1993}.
